Formalizing Stack Safety as a Security Property

### 2022-08-26 submission5/onlyformalism.tex
Last night's changes

\begin{align*}
\psi \in \Psi ::= & \mathbf{call} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{tailcall} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{return} & \\
| & \mathbf{alloc} ~ size ~ public & size \in \mathbb{N}, public \in \mathbb{B} \\
| & \mathbf{setex} \\
| & \mathbf{throwex} \\
\end{align*}

@@

>>>>

\begin{align*}
\psi \in \Psi ::= & \mathbf{call} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{tailcall} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{return} & \\
| & \mathbf{alloc} ~ size & size \in \mathbb{N} \\
| & \mathbf{setex} \\
| & \mathbf{throwex} \\
\end{align*}

@@

Alloc macro-instructions model allocations that might, or might not, be
shared. A function can always allocate more opjects by adjusting its
stack pointer outside of a macro-instruction, but this will not be reflected
in the context.
